---
title: "inference-demo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{inference-demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LMkesslerd)
```
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Simulate Data
Suppose we have a simple linear model with two predictors:

```{r}
n <- 100
X <- cbind(1, rnorm(n), rnorm(n))  # Intercept, X1, X2
beta <- c(2, 1, -1)
sigma <- 1
y <- X %*% beta + rnorm(n, sd = sigma)
```

# OLS Estimation
Estimate the regression coefficients using `find_beta`:

```{r}
beta_hat <- find_beta(y, X)
beta_hat
```

# Confidence Interval for a Linear Combination
Construct a 95% confidence interval for $\beta_2$ (the coefficient of X1):

```{r}
gamma <- c(0, 1, 0)  # Selects beta_2
ci_beta2 <- make_CI(y, X, alpha = 0.05, gamma = gamma)
ci_beta2
```

# Constrained Estimation
Suppose we want to estimate the coefficients under the constraint $\beta_2 + \beta_3 = 0$:

```{r}
C <- matrix(c(0, 1, 1), nrow = 1)  # Constraint: beta_2 + beta_3 = 0
d <- 0
beta_hat_H <- find_betaH(y, X, C, d)
beta_hat_H
```

# F-test for Linear Restrictions (RSS method)
Test the null hypothesis $H_0: \beta_2 + \beta_3 = 0$ using the F-test based on RSS:

```{r}
f_rss <- f_test_RSS(y, X, C, d)
f_rss
```

# F-test for Linear Restrictions (Quadratic form)
Alternatively, use the quadratic form for the same test:

```{r}
f_quad <- f_test_quad(y, X, C, d)
f_quad
```
